### 2021-05-20 doc/thesis/chapters/dsp.tex
move overview

On the receiver side, once the signal reaches the antenna of a receiver, there are further similarities.
In order to decode the actual data content of the signals, they need to be converted down to become a baseband signal.
Again, there are multiple ways to achieve that.
In baseband, the signal can then be further processed, until the data content of interest is visible.

The block diagram in Fig.\ref{fig:bd_dsp_overview} gives a high-level overview of a receiver structure.

\includepicture [0.5] [0] {An overview of the signal processing chain.} {bd_dsp_overview} {img/draw.io/bd_dsp_overview}

% TODO: block diagram of receiver
% Antenna -->
% --> Analog Frontend (gain, filter, mixer to baseband)
% --> Digital Signal Processing
% --> Output (e.g. speakers)

>>>>

On the receiver side, once the signal reaches the antenna of a receiver, there are further similarities.
The antenna signal needs to be amplified and filtered.
Both steps depend on the antenna characteristics, but usually the received signal is of relatively low power, and the antenna receives a wider range of frequencies than required.
The filter therefor selects the frequency area that is of interest.
Another reason for the filter is to avoid spectral replicas in the subsequent modulation, or down-conversion.
Here, the front-end often down-converts to a low intermediate frequency, instead of directly going to baseband.
The intermediate frequency is then modulated, or mixed, down to baseband later in the digital domain, which brings advantages in the downstream processing chain. %TODO check this or explain more which advantages (HF to BB directly --> i/q complex signal? ; HF to IF to BB --> real signal ) ??

These three steps - amplification, filtering and down-conversion - are usually done in the analog domain, since digital circuits cannot work with such high frequencies.
After the analog signal is down-converted to baseband, it needs to be digitized.
This is done by an analog-digital-converter (ADC).

After the signal is processed to digital baseband, the received signal can finally be decoded to get the actual data content.
This decoding process depends on the respective modulation type that is used.\\

\noindent
The block diagram in Fig.\ref{fig:bd_dsp_overview} gives a high-level overview of a receiver structure.

\includepicture [1.0] [0] {An overview of the signal processing chain.} {bd_dsp_overview} {img/draw.io/bd_dsp_overview}
